
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Matthew S. Bane}  & 312-420-6473 (cell)\\
1750 N. Cleveland Ave. &  matthewsbane@gmail.com \\
Unit B & http://www.matthewsbane.com/\\
Chicago, IL 60614 & https://www.linkedin.com/in/matthewscottbane
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{DePaul University, School of Computing and Digital Media}{Chicago, IL}
	{Master of Science in Computer Science}{June 2014}
	\begin{itemize}
		\resitem{Concentration in Artificial Intelligence}
\end{itemize}
\item
	\ressubheading{University of Pennsylvania, Wharton School}{Philadelphia, PA}
	{Bachelor of Science in Economics}{December 2000}
	\begin{itemize}
		\resitem{Concentration in finance}
	\end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Conversant, LLC.}{Chicago, IL}{Software Engineer - Ad Server}{September 2014 - Present}
	\begin{itemize}
		\resitem{Design and implement new features and enhancements on a distributed ad-server delivering real-time digital advertisements.}
		\resitem{Work with other engineers and product managers to establish and refine clear requirements which align with business goals.}
		\resitem{Write robust, high-performance code for a high throughput, low latency system.}
		\resitem{Write unit tests, test code in production environment, work with QA to create new tests and ensure coverage for all existing and new features in QA environment.}
		\resitem{Work with product managers to verify releases of new features and troubleshoot any production issues.}
		\resitem{Conduct performance testing and monitoring of production systems.}
	\end{itemize}
\item
	\ressubheading{M\&N Trading}{Chicago, IL}{Quantitative Trader and Software Developer}{February 2013 - September 2013}
	\begin{itemize}
		\resitem{Traded U.S. fixed income cash and futures markets using an automated statistical arbitrage 
   trading strategy.}
		\resitem{Developed trading algorithms in C\# using CQG Trading API.}
		\resitem{Used R to perform data analysis, build experimental trading models, and extract data from 
   Microsoft Access database.}
		\resitem{Created XML files and wrote code to serialize and transfer data between various applications. }
	\end{itemize}
\item
	\ressubheading{Hard Eight Futures, LLC}{Chicago, IL}{Quantitative Trader and Software Developer}{April 2012 - January 2013}
	\begin{itemize}
		\resitem{Researched, developed, and traded automated applications in the U.S. fixed income cash and 
   futures markets and U.S. equity futures markets using a statistical arbitrage trading strategy.}
		\resitem{Development done in C\# with Trading Technologies, TT API.}
		\resitem{Applied various financial data analysis and modeling techniques to price futures markets with 
   a term-structure, reducing dimensionality and facilitating computation.}
        \resitem{Implemented and maintained a Microsoft Access database to warehouse extensive amounts of financial data.}
	\end{itemize}
\item
	\ressubheading{Gelber Group, LLC.}{Chicago, IL}{Quantitative Trader and Software Developer}{March 2008 - August 2009}
	\begin{itemize}
		\resitem{Researched, developed, and traded automated mid-frequency trading applications for FX cash and 
   futures markets, crude oil, natural gas, corn, soy bean, and wheat futures markets.}
		\resitem{Utilized GVelocity a proprietary trading API written in C\# to develop applications.}
		\resitem{Performed various financial data analysis using excel with a Bloomberg add-in to extract historical price data and other related financial data.}
	\end{itemize}

\item
	\ressubheading{Gelber Group, LLC.}{Chicago, IL}{Proprietary Trader}{June 2002 - December 2008}
	\begin{itemize}
		\resitem{Managed a trading account specializing in U.S. and European fixed income, equity, commodity
   derivatives (futures and options), and their underlying cash instruments.}
		\resitem{Employed methods of relative value, statistical arbitrage, and market making to take advantage 
   of short-term price discrepancies.}
		\resitem{Utilized mean reversion and pairs trading for multi-day strategies.}
		\resitem{Performed daily statistics to monitor profitability and risk. }
	\end{itemize}

\item
	\ressubheading{Group One Trading LP}{Chicago, IL}{Trader Trainee, Chicago Board Options Exchange}{January 2001 - January 2002}
	\begin{itemize}
		\resitem{Assisted traders with risk management activities updating delta, gamma, theta, and vega
  parameters and applying appropriate underlying hedge for multiple equity options.}
		\resitem{Updated traders’ positions to reflect current market volatility estimates.}
	\end{itemize}

\end{itemize}

\resheading{Technical Skills}

\begin{description}
\item[Languages:]
Java, C{}\verb!#!, Python, SQL, R, Bourne Again Shell, Sed, Awk, Grep, HTML, XML, JSON, EXCEL
\item[Technologies:]
Kafka, Simple Binary Encoding(sbe), flatbuffers, Protocol Buffers, JAX-RS, JAX-WS, Jetty, Netty, JMH, Trove, Docker
\item[Operating Systems:]
Linux, Windows
\item[IDE:]
Intellij, Eclipse, Vi, Visual Studio
\item[Project Management:]
Git, Jira, Bamboo, Confluence, Kanban, Scrum, Agile Development
\item[Miscellaneous:]
Excellent troubleshooting and debugging skills
\end{description}

%\resheading{}

%\begin{description}
%\item[]
%\item[]
%\end{description}

\end{document}
